\disstitle

### 2018-06-12 chapters/introduction/introduction.tex
camera geometry

%Outline:
\begin{itemize}
  \item sliver bullet and ``summer project'' story
  \item ``summer project'' is still going on
  \item tranditional CV methods and emerge of deep learning (gamer changer)
  \item geometry information are useful for applications, how to learn them
  \item geometry information are useful for image understanding (training), how to use them
  \item overhead image (encoding location) as type of geometry information are useful
  \item growing, densely available in space and time
\end{itemize}

@@

\brief{
The ultimate goal of image understanding is to extract high-level
understanding from digital images or videos. The task seems natural
and easy for an adult human, but it is difficult for machines. 1) Silver
bullet does not exist \todo{cite}, no general algorithm, we do things
in a ad-hoc manner.
}

@@

  \item \textbf{Camera Geometry for Image Understanding:}
  We explore the potentials of camera geometry for image understanding.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.

>>>>

%Outline:
\begin{itemize}
  \item sliver bullet and ``summer project'' story
  \item Geometry is important.
  \item traditional method for geometry detection
  \item deep learning (gamer changer)
  \item geometry detection with deep learning
  \item geometry for deep learning training
  \item overhead images
\end{itemize}

@@

It is not a trivial task for machines to understand images in general.
To achieve this goal, researchers adopt a divide-and-conquer strategy,
that is divide image understanding into various sub-problems like
object recognition, semantic segmentation, and pose estimation \etc.
During the past decades, a lot of methods are developed to solve there
sub-problem, many of them adopted a bottom-up (\todo{citations})
workflow, where basic level cues play important roles
(\todo{examples}). Among there basic cues, camera geometry are
particularly useful for some computer vision tasks like facade
detection, indoor layout estimation~\cite{ren2016coarse}.

In the camera pin-hole model, camera geometry denotes the camera
both intrinsic and extrinsic parameters. The intrinsic parameters
encode the information of the camera itself such as focal length,
principal point \etc; the extrinsic parameters are referred to as the
external states of the camera, such as the camera poses and
offset/location under some coordinate system. In this work, our study
of the camera geometry mainly includes the extrinsic like camera pose
and the geo-orientation/geo-localization of the camera.

@@

  \item \textbf{Camera Geometry for Image Understanding:}
  \todo{more writing}
  We explore the potentials of camera geometry for image understanding.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
